Getting Data from World Bank          purple book pg39, 13.6.15
========================================================

ref: data.worldbank.org

Example: I can download a csv of net migration by going to data.worldbank.org/indicator and choosing 'net migration' under the Aid Effectiveness header. Then choose 'download data' which can be either excel, xml or csv
```{r}
csvFilename <- '/Users/jamesmungall/MyR/GettingCleaningData/data/worldBank/netMigration.csv'
netMigration <- read.csv(csvFilename, stringsAsFactors=F, skip=2); # There are two title lines to ignore
```
Or you can download the excel file.
```{r}
excelFilename <- '/Users/jamesmungall/MyR/GettingCleaningData/data/worldBank/netMigration.xls'
library(xlsx)
netMigration2 <- read.xlsx(excelFilename,sheetIndex=1,startRow=2);# Ignore first row
View(netMigration2)
```

The code below successfully downloads a table of the Lower Middle Income countries
```{r}
url <- 'http://api.worldbank.org/countries?incomeLevel=LMC&format=json'
savedFile <- "/Users/jamesmungall/MyR/GettingCleaningData/data/worldBank/incomeLevelLMC.json"
download.file(url, destfile = savedFile, method = "curl")
library(jsonlite)
jsonData <- fromJSON(savedFile)
View(jsonData)
```
