---
title: "Exporatory Factory Analysis"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
https://www.promptcloud.com/blog/exploratory-factor-analysis-in-r/

##### Exploratory Factor Analysis, 30th June 2018
### Analysis of dataset using psych and GPArotation packages

Open EFA.csv file and tore as a variable called data

data <- read_delim("p65 Exploratory Factor Analysis/EFA.csv")
```{r}
View(data)
```
install.packages('psych')
install.packages('GPArotation')
library(psych)
library(GPArotation)


##Parallel Analysis - to determine max no. factors
```{r}
parallel <- fa.parallel(data, fm = 'minres', fa = 'fa')
```
Output states: 'Parallel analysis suggest that the number of factors is 5'

## Factor Analysis - to determine the best number of factors and their meanings.
```{r}
threefactor <- fa(data,nfactors = 3,rotate = "oblimin",fm="minres")
print(threefactor)
fourfactor <- fa(data,nfactors = 4,rotate = "oblimin",fm="minres")
print(fourfactor)
print(threefactor$loadings,cutoff = 0.3)
print(fourfactor$loadings,cutoff = 0.3)
```
We see a simpler structure with three factors. Look for a low root mean square residual and high Tucker-Lewis Index for good adequacy.

## Naming the factors

We may classify the factors as MR1 = price, MR2 = quality, MR3 = reviews
