Joins                 purple book p38  11.6.15
========================================================
ref: Data Wrangling with dplyr and tidyr Cheat Sheet

table 'a'           table 'b'
  x1 | x2             x1 | x3
  --------------------------
1  A |  1             A |  TRUE
2  B |  2             B | FALSE
3  C |  3             D |  TRUE
```{r}
x1 <- c('A','B','C')
x2 <- c(1,2,3)
a <- data_frame(x1,x2)
x1 <- c('A','B','D')
x3 <- c(T,F,T)
b <- data_frame(x1,x3)
```
We can retreive x3 values from b reference by x1 values from a
```{r}
left_join(a,b,by='x1')
```
  x1 x2    x3
1  A  1  TRUE
2  B  2 FALSE
3  C  3    NA

A more complicated example may be

table 'a'       table 'b'
id    name      id    maths_score
1     Adam      1     67
2     Bill      2     91
3     Colin     3     33

Therefore information about a name or maths score can be combined by id so that we know who scored well on the maths test.
```{r}
name <- c('Adam','Bill','Colin')
id <- c(1,2,3)
a <- data_frame(id,name)
id <- c(1,2,3)
maths_score <- c(67,92,33)
b <- data_frame(id,maths_score)
left_join(a,b,by='id')
```
  id  name maths_score
1  1  Adam          67
2  2  Bill          92
3  3 Colin          33

