Access to Water                   Purple book pg 41, 17.6.15
=================================================================
ref: rpubs.com/justmarkham/dplyr-tutorial
    data.worldbank.org  

population
==========
Create table of population for each region / income level combination
```{r}
library(jsonlite)
library(dplyr)
library(tidyr)
populationUrl <- 'http://api.worldbank.org/countries/indicators/SP.POP.TOTL?per_page=1000&date=2013&format=json'
populationFile <- "/Users/jamesmungall/MyR/GettingCleaningData/data/worldBank/population/population.json"
download.file(populationUrl, destfile = populationFile, method = "curl")
jsonPopulation <- fromJSON(populationFile)
population <- jsonPopulation[[2]][-(1:34),] %>%
  flatten() %>% tbl_df() %>%
  transmute(country.value, pop=as.numeric(value))
```
countries
=========
```{r}
countriesUrl <- 'http://api.worldbank.org/countries?format=json&per_page=1000'
countriesFile <- "/Users/jamesmungall/MyR/GettingCleaningData/data/worldBank/countries.json"
download.file(countriesUrl, destfile = countriesFile, method = "curl")
jsonData <- fromJSON(countriesFile)
countries <- jsonData[[2]] %>%
  flatten() %>% tbl_df() %>%
  select(country.value=name,region.id,incomeLevel.id)
```  
popRegionIncome
===============
combine population and region/incomeLevel data
```{r}
popRegionIncome <- left_join(population,countries,by='country.value')
View(popRegionIncome)
```

accessToImprovedWater
==================
Use http://www.wssinfo.org/data-estimates/tables/ to select data.
Export as '/Users/jamesmungall/MyR/GettingCleaningData/data/accessToImprovedWater.csv'

```{r}
library(jsonlite)
library(dplyr)
library(tidyr)
filename = '/Users/jamesmungall/MyR/GettingCleaningData/data/accessToImprovedWater.csv'
waterData <- read.csv(filename, stringsAsFactors=F)
accessToImprovedWater <- waterData[4:238,]
accessToImprovedWater <- accessToImprovedWater %>% flatten() %>% tbl_df() %>%
  transmute(country.value=X, waterPerc = as.numeric(Water))
View(accessToImprovedWater)
```

popWater
======
```{r}
popWater <-  left_join(popRegionIncome,accessToImprovedWater,by='country.value') %>%
  mutate(waterPop = pop * waterPerc/100) %>%
  group_by(region.id,incomeLevel.id)


popWater2 <- popWater[complete.cases(popWater),] %>%
  summarise_each(funs(sum), totalPop=pop,waterPop) %>%
  mutate(waterPerc = (100 * waterPop / totalPop)) %>%
  select(region.id,incomeLevel.id,waterPerc) %>%
  spread(key=region.id,value=waterPerc)
View(popWater2)
```

