PopWaterElec                              PurpleBook pg42  19.6.15
==================================================================

ref: rpubs.com/justmarkham/dplyr-tutorial
    data.worldbank.org  
    http://www.wssinfo.org/data-estimates/tables/
    
    
regionIncomeDf
============
```{r}
library(jsonlite)
library(dplyr)
library(tidyr)
regionIncomeUrl <- 'http://api.worldbank.org/countries?format=json&per_page=1000'
regionIncomeFile <- "/Users/jamesmungall/MyR/GettingCleaningData/data/worldBank/countries.json"
download.file(regionIncomeUrl, destfile = regionIncomeFile, method = "curl")
jsonRegionIncome <- fromJSON(regionIncomeFile)
regionIncomeDf <- jsonRegionIncome[[2]] %>%
  flatten() %>% tbl_df() %>%
  select(country.value=name,region.id,incomeLevel.id) %>%
  filter(region.id != 'NA')
View(regionIncomeDf)
```
populationDf
============
```{r}
populationUrl <- 'http://api.worldbank.org/countries/indicators/SP.POP.TOTL?per_page=1000&date=2010&format=json'
populationFile <- "/Users/jamesmungall/MyR/GettingCleaningData/data/worldBank/population/population.json"
download.file(populationUrl, destfile = populationFile, method = "curl")
jsonPopulation <- fromJSON(populationFile)
populationDf <- jsonPopulation[[2]][-(1:34),] %>%
  flatten() %>% tbl_df() %>%
  transmute(country.value, pop=as.numeric(value))
View(populationDf)
```
percElecDf
==========
```{r}
elecUrl<-'http://api.worldbank.org/countries/indicators/EG.ELC.ACCS.ZS?per_page=1000&date=2010&format=json'
elecFile <- "/Users/jamesmungall/MyR/GettingCleaningData/data/worldBank/accessToElectricity/accessToElectricity.json"
download.file(elecUrl, destfile = elecFile, method = "curl")
elecData <- fromJSON(elecFile)
percElecDf <- elecData[[2]][-(1:34),] %>% flatten() %>% tbl_df() %>%
  transmute(country.value, elecPerc = as.numeric(value))
View(percElecDf)
```
percWaterDf
===========
Use http://www.wssinfo.org/data-estimates/tables/ to select data.
Export as '/Users/jamesmungall/MyR/GettingCleaningData/data/accessToImprovedWater.csv'
```{r}
filename = '/Users/jamesmungall/MyR/GettingCleaningData/data/accessToImprovedWater.csv'
waterData <- read.csv(filename, stringsAsFactors=F)
percWaterDf <- waterData[4:238,]
percWaterDf <- percWaterDf %>% flatten() %>% tbl_df() %>%
  transmute(country.value=X, waterPerc = as.numeric(Water))
percWaterDf <- percWaterDf[complete.cases(percWaterDf),]
View(percWaterDf)
```
join to make popElecWaterDf
===========================

```{r}
popElecWaterDf1 <- left_join(regionIncomeDf,populationDf)
popElecWaterDf2 <- left_join(popElecWaterDf1,percElecDf)
popElecWaterDf3 <- left_join(popElecWaterDf2,percWaterDf)
# Turn percentages to populations
popElecWaterDf <- popElecWaterDf3 %>% mutate(elecPop = pop * elecPerc/100, waterPop = pop * waterPerc/100) %>%
  select(region.id,incomeLevel.id,pop,elecPop,waterPop)
View(popElecWaterDf)
```
Group by region and sum to make gpPopElecWaterDf
================================================
```{r}
gpPopElecWaterDf <- popElecWaterDf %>% group_by(region.id,incomeLevel.id) %>%
  summarise_each(funs(sum(.,na.rm=T)),pop,elecPop,waterPop) %>%
 mutate(percElec = elecPop * 100 / pop, percWater = waterPop * 100 / pop)
View(gpPopElecWaterDf)
```
Filter to remove small (< 1/10th of largest group population) groups, filterPopElecWaterDf
```{r}
largestGroupPopulation <- max(gpPopElecWaterDf$pop)
filterPopElecWaterDf <- gpPopElecWaterDf %>% filter(pop > largestGroupPopulation / 10) %>%
  select(incomeLevel.id,pop,percElec,percWater)
View(filterPopElecWaterDf)
```



